Compare pseqs

### 2019-05-15 comparepseqs.Rmd
Bray matrix

>>>>

```{r matrix calculation}
if (!file.exists("rds/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = 4)
    saveRDS(bray.dist.matrix, file = "rds/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds/comparepseqs_bray_matrix.rds")
}
```

 ```{r adonis calculation, eval = FALSE}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 1000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
                                                          "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 1000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
